### 2011-05-13 paper/paper.tex
added citation about estimating volume

We consider the problem of randomly and uniformly sampling a point from a convex region in $n$-dimensional space. This has applications, for instance, in convex optimization \cite{Dabbene}. Sampling can also allow us to estimate the volume of a convex region \cite{Dyer}.

@@

>>>>

We consider the problem of randomly and uniformly sampling a point from a convex region in $n$-dimensional space. This has applications, for instance, in convex optimization \cite{Dabbene}. Sampling can also allow us to estimate the volume of a convex region (\cite{Dyer}, \cite{Vempala2}).

@@

\bibitem{Vempala2} Lov\'asz, L. and Vempala, S. ``Simulated Annealing in Convex Bodies and an $O^*(n^4)$ Volume Algorith." Journal of Computer and System Sciences, Vol. 72, Issue 2, March 2006.
